Definitions:
\Hrule
\halign{{\it #}\hfil&\vtop{\parindent=0pt\hsize=1.6in\strut#\strut}\cr
Loop &An edge connecting a vertex to itself.\cr
Directed &Each edge has a direction.\cr
Simple &Graph with no loops or multi-edges.\cr
Walk &A sequence $v_0e_1v_1\ldots e_\ell v_\ell$.\cr
Trail &A walk with distinct edges.\cr
Path &A trail with distinct vertices.\cr
Connected &A graph where there exists a path between any two vertices.\cr
Component &A maximal connected subgraph.\cr
Tree &A connected acyclic graph.\cr
Free tree &A tree with no root.\cr
DAG &Directed acyclic graph.\cr
Eulerian &Graph with a trail visiting each edge exactly once.\cr
Hamiltonian &Graph with a cycle visiting each vertex exactly once.\cr
Cut &A set of edges whose removal increases the number of components.\cr
Cut-set &A minimal cut.\cr
Cut edge &A size 1 cut.\cr
k-Connected &A graph connected with the removal of any $k-1$ vertices.\cr
k-Tough &$\forall S \subseteq V, S \neq \emptyset$ we have \hbox{$k\cdot c(G-S) \leq \vert S \vert$}.\cr
k-Regular &A graph where all vertices have degree $k$.\cr
k-Factor &A $k$-regular spanning subgraph.\cr
Matching &A set of edges, no two of which are adjacent.\cr
Clique &A set of vertices, all of which are adjacent.\cr
Ind. set &A set of vertices, none of which are adjacent.\cr
Vertex cover &A set of vertices which cover all edges.\cr
Planar graph &A graph which can be embeded in the plane.\cr
Plane graph &An embedding of a planar graph.\cr
}
\Hrule
$$ \sum_{v\in V} \deg(v) = 2 m.$$
If $G$ is planar then $n - m + f = 2$, so
$$
f \leq 2n - 4, \quad m \leq 3 n - 6.
$$
Any planar graph has a vertex with degree $\leq 5$.
